---
title: "HE3021 Tutorial 1 Attempt"
author: "Lui Yu Sen"
date: "1/20/2021"
output: pdf_document
---

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("foreign")
library("ggplot2")
library("lmtest")
library("sandwich")
```

```{r filepath, echo=FALSE}
fil <- 
    "C:\\Users\\Lui Yu Sen\\Google Drive\\NTU_study materials\\Economics\\HE3021 Intermediate Econometrics\\Week 1\\HE3021-Week-1-Tutorial-1\\rawdata\\bwght2.dta"
```

Initial reading of raw data. Packages used are tidyverse, foreign, ggplot2, sandwich and lmtest.

```{r init_read, echo=TRUE}
dat <- read.dta(file = fil)
dat <- mutate(dat, npvis_squared = npvis**2)

model <- lm(bwght ~ npvis + npvis_squared + cigs + male, dat)
```

# (a)
```{r part_a, echo=TRUE}
mean_med <- summary(dat[, "bwght"])
mean_bwght <- mean_med[4]
print(mean_bwght)
```

# (b)
```{r part_b, echo=TRUE}
med_bwght <- mean_med[3]
print(med_bwght)
```

# (c)
```{r part_c, echo=TRUE}
plot_bwght <- ggplot(dat, aes(x = bwght)) + 
    geom_histogram(binwidth = 100, color = "black")
print(plot_bwght)
```

# (d)
```{r part_d, echo=TRUE}
beta_3 <- model$coefficients["cigs"]
print(beta_3)
```

# (e)
$H_0:\beta_3=-10$, $H_a:\beta_3\neq-10$, $\alpha=0.05$, 2-tailed 1-sample t-test.
```{r part_e, echo=TRUE}
t_test_2tail_variable_hypo <- function(
    hypothesis, significance_lvl, df, sample_value, standard_error){
    confidence_interval <- hypothesis +c(-1, 1)*qt(p = 1-significance_lvl/2,
                                            df = df)*standard_error
    if (between(sample_value, confidence_interval[1], confidence_interval[2])){
        return(FALSE)
    } else {return(TRUE)}
}
test_beta_3 <- t_test_2tail_variable_hypo(
    -10, 0.05, 1651, beta_3, 3.3330) # TRUE means insignificantly different from -10
confidence_interval <- -10 + c(-1, 1)*qt(p = 0.975, df = 1651)*3.3330
print(confidence_interval)
```
Since $\beta_3\in[-16.54,-3.46]$, then we have insufficient evidence to reject $H_0=-10$.

# (f)
$H_0:\beta_4=100$, $H_a:\beta_4\neq100$, $\alpha=0.05$, 2-tailed 2-sample Welsh t-test.
```{r part_f, echo=TRUE}
test_beta_4 <- t_test_2tail_variable_hypo(
    100, 0.05, 1651, beta_3, 27.9757) # TRUE means insignificantly different from +100
confidence_interval <- 100 + c(-1, 1)*qt(p = 0.975, df = 1651)*27.9757
print(confidence_interval)
```
Since $+100\in[45.1,154.9]$, then we have insufficient evidence to reject $H_0=+100$.

# (g)
```{r part_g, echo=TRUE}
beta_1 <- model$coefficients["npvis"]
beta_2 <- model$coefficients["npvis_squared"]
```
The partial effect is $32.8npvis+(-0.669)npvis^2$.

# (h)
$0=\frac{\partial bwght}{\partial npvis}=32.8+(-0.669)npvis*2$,
$npvis=\frac{32.8}{2*(0.669)}$
```{r part_h, echo=TRUE}
turning_pt <- beta_1/(2*-beta_2)
print(turning_pt)
```
$npvis= 24.50519$
Diminishing marginal returns of additional pre-natal visits since there is not much more the doctor can check.

# (i)
$H_0:0=\beta_1=\beta_2=\beta_3=\beta_4$, $H_a:otherwise$, F-test of squared residuals against independent variables.
```{r part_i, echo=TRUE}
hetero_test <- model$model[, 2:5]
hetero_test <- mutate(hetero_test, residuals = model$residuals)
hetero_test <- mutate(hetero_test, residuals = residuals**2)
hetero_test_model <- lm(residuals ~ npvis + npvis_squared + cigs + male, hetero_test)
hetero_test_p_value <- 4.476*(10**(-5)) # heteroscedastic
```
Since $4.476*(10^{-5})<0.05$, then we have sufficient evidence to reject $H_0$, and we cannot have the homoscedascity assumption.
To solve it, we can use robust standard errors as sample size $n=1656>120$. The hypothesis tests for $\beta_3$ and $\beta_4$ would then be like so:
```{r robust_tests, echo=TRUE}
robust_t <- coeftest(model, vcov = vcovHC(model, type = "HC0"))
print(robust_t)
test_beta_3_robust <- t_test_2tail_variable_hypo(
    -10, 0.05, 1651, beta_3, 3.28212) # TRUE means insignificantly different from -10
confidence_interval <- -10 + c(-1, 1)*qt(p = 0.975, df = 1651)*3.28212
print(confidence_interval)
test_beta_4 <- t_test_2tail_variable_hypo(
    100, 0.05, 1651, beta_3, 27.82588) # TRUE means insignificantly different from +100
confidence_interval <- 100 + c(-1, 1)*qt(p = 0.975, df = 1651)*27.82588
print(confidence_interval)
```
Since $-10\in[-16.437556,-3.562444]$, then we cannot reject $H_0:\beta_3=-10$.
Since $+100\in[45.42227,154.57773]$, then we cannot reject $H_0:\beta_4=100$.

# (j)

No, I do not think we can have the zero conditional mean, because income can be correlated with pre-natal visits since poorer people can come from locations where clinics are inaccessible. Income itself can influence mother's nutrition, which can influence baby weight.